Model Establishment for AMZN Stock

### 2017-06-14 code/Prediction.Rmd
Add files via upload

m1 = garchFit(~1 + garch(1,0), data = lgreturn,trace=F) # Fit an ARCH(1) model
summary(m1)

m2 = garchFit(~1 + garch(1,1), data = lgreturn,trace=F) # Fit a GARCH(1,1) model
summary(m2)

@@

>>>>

m1 = garchFit(~1 + garch(1,0), data = lgreturn/100,trace=F) # Fit an ARCH(1) model
summary(m1)

m2 = garchFit(~1 + garch(1,1), data = lgreturn/100,trace=F) # Fit a GARCH(1,1) model
summary(m2)

@@

## Predict
```{r, echo=TRUE, message=FALSE, warning=FALSE}
sigma2=predict(m2,50)
print(sigma2)
library(sciplot)
plot(sigma2$meanForecast,ylim=c(-0.05,0.05))
lines(c(1:50),sigma2$meanForecast+1.96*sigma2$meanError,col='blue')
lines(c(1:50),sigma2$meanForecast-1.96*sigma2$meanError,col='blue')
```
